---
title: "Final Project"
author: "David Cobb"
date: "March 23, 2019"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    runtime: shiny
---

```{r setup, include=FALSE}
library("flexdashboard")
library("MASS")
library("tidyverse")
library("broom")
library("glmnet")
library("caret")
library("ISLR")
library("janitor")
library("stringr")
library("randomForest")
library("nnet")
library("car")
library("GGally")
library("xtable")
library("rpart")
library("rpart.plot")
library("glmnet")
theme_set(theme_bw())
```


```{r data}
# Read Raw Data
fars_raw <- read_csv("../project/car-safety-fars-backup.csv")
fars <- read_csv("../project/car-safety-fars.csv")
fars_summary <- read_csv("../project/car-safety-fars-cleaned-data.csv")
```

```{r}
# Add MAKE_MODEL column to the raw data
fars = mutate(fars,
   MAKE_MODEL = paste(VINMAKE_T, VINMODEL_T, sep = '_'))
```

```{r}
# Create Training and Testing Data
set.seed(1)
df_fars <- tbl_df(fars)
inTraining <- createDataPartition(df_fars$Fatal_Injury, p = .50, list = F)
                                  training <- df_fars[inTraining,]
                                  testing <- df_fars[-inTraining,]
```

Page 1 - Summary Table
=====================================  

```{r}
fars_filter <- filter(fars_summary, MAKE_MODEL != "_")
by_make_model <- group_by(fars_filter, MAKE_MODEL,DRIVETYP, DISPCLMT, TURBO_T, SUPCHRGR_T)
new <- summarize(by_make_model, 
                 fatals = sum(Fatal_Injury),
                 injuries = sum(Suspected_Minor_Injury + Suspected_Serious_Injury),
                 no_injury = sum(No_Apparent_Injury))
renderDataTable(new)
```

Page 2 - Summary Charts {data-orientation=rows}
=====================================     

### Chart 1 
```{r}
chart1 <- ggplot(data = new) +
  #geom_point(mapping = aes(x = DRIVETYP, y = fatals)) +
  geom_col(mapping = aes(x = DRIVETYP, y = fatals)) +
  theme_light()
chart1
```

### Chart 2

```{r}
chart2 <- ggplot(data = fars, 
            aes(x = Fatal_Injury, y = DISPCLMT))
chart2 + geom_violin(alpha = .15) +
  scale_color_brewer(palette = "Dark2") +
  guides(col = F)
```
   
Page 3 - Summary Charts 2  {data-orientation=rows}
=====================================  

### Chart 4 - Fatal Injuries Compared to Drive Type and Displacement
```{r}
fars_displacement <- filter(fars, DISPCLMT != "NA")
chart4 <- ggplot(data = fars_displacement,
            aes(x = Fatal_Injury, y = DISPCLMT, fill = DRIVETYP)) +
theme(legend.position="bottom")
chart4 + geom_violin() 
```   
    
### Chart 5 - Scatter Chart of Fatal Injuries compared to Engine Size
```{r}
chart5 <- ggplot(new, aes(x = DISPCLMT, y = fatals)) +
  geom_point() +
  scale_x_discrete(labels = abbreviate) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
chart5
```

Page 4 - Logistic Regression
=====================================  
### Logistic Regression Using 4 Variables
```{r}
lrm <- tidy(glm(Fatal_Injury ~ DRIVETYP + DISPCLMT + TURBO_T + SUPCHRGR_T + MAKE_MODEL, data = fars))
renderDataTable(lrm)
```

Page 5 - Summary Logistic Regression
=====================================  
### Information about the model
```{r}
summary(lrm)
```

Page 6 - Tree Attempt
=====================================  
### Using 6 variables MAKE_MODEL + DRIVETYP + DISPCLMT + TURBO_T + SUPCHRGR_T
```{r}
first_tree <- tree::tree(Fatal_Injury ~ DRIVETYP + DISPCLMT + TURBO_T + SUPCHRGR_T + VINMAKE_T + VINMODEL_T + SUPCHRGR_T + ORIGIN_T + SHIPWEIGHT + RSTRNT_T, 
                         data = fars_raw,
                         minsize = 100)
plot(first_tree)
text(first_tree, cex=.75)
```

### Summary
```{r}
summary(first_tree)
```

Page 6 - Another Chart
=====================================  
### Fatals by Drive Type and Turbo Charged
```{r}
chart3 <- ggplot(data = fars_filter) +
  geom_point(aes(x = DRIVETYP,  y = TURBO_T,  size = Fatal_Injury)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
chart3
```

Page 7 - Methodology
=====================================  
### Notes on the process
### Overall Notes
1)  Obtained Fatal Accident Reporting System data for 2016 (FARS)
2)  Obtained Crash Estimate Data for 2016 (CRSS)
3)  Merged columns from 3 tables in each set to create a crash, person, vehicle data set
    A)  Contains, for each person in the crash, the outcome including; Fatality, Injured, Not Injured
    B)  Contains VIN information for some of the vehicles
4)  Data was parsed to one row per person making a binary indicator for each outcome listed above
5)  Various charts and tables to understand the data
6)  Multiple logistic regression model run to determine if any of the variables are significant and does the data suggest there is a relationship between them and the fatality outcome

### Data Observations
1)  The data set of 100k records and 127 columns was challenging to work with at my level
2)  Had originally planned to join a sample data set, CRSS, to the fatal data set.  There is a way to estimate the number of crashes per Make Model but proved to be out of scope for me.
3)  This left me with the Fatal Crash data set only.
    --> There is still hope as each person in each crash with a fatality is in the data, meaning many people walked away.  About 1/3 didn't make it.  This allows us to compare the Fatal outcomes by vehicle make model and a few other performance attributes

### Regression Observations
Does performance matter?  Does make and model matter?
1)  Turbos might matter, but we need more data to tell
2)  A short list of Make Models show up with significant P-Values, suggesting there are differences between make and models in terms of fatal outcomes.  Again, really need more data as we can't tell how significant the fatal accidents are without more crash data.  Roughly 35k fatalities and 7.5 million crashes.  Since the goal of this is to determine if the make model and performance characteristics are significant, more data is needed to understannd how accidents play out across the make x model population (1000s of combinations)
3)  Other factors included in the analysis don't suggest there a relationship to the target variable
4)  The overall conclusion is that this to go another layer deeper, and needs to leverage 'big data' to truly understand how safe our cars are and whether or not certain cars are very dangerous.
